---
title: <center><h1>Extra Plots</h1></center>
author: 
output:
  html_document: 
    toc: false
    theme: flatly
    toc_float: true
    collapsed: true
    number_sections: false
    toc_depth: 1
editor_options: 
  chunk_output_type: inline
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
library(ggplot2)
library(tidyverse)
library(gridExtra)
library(dplyr)
library(plotly)
library(itertools)
library(scales)
library(forecast)
library(Rtsne)
library(benford.analysis)

```


```{r 1, echo=FALSE, cache=FALSE, fig.align='left', fig.height=4.5, fig.width=9, results='show'}


# # WESTERN EURO DATA DAY
# 
# fr = read.csv("eurodata/fr.csv", header =TRUE, stringsAsFactors = FALSE)
# fr$end = fr$end %>% as.Date()
# fr = aggregate(fr["load"], by=fr["end"], sum)
# fr = fr[1:(length(fr$load)-1),]
# df = fr
# setwd("eurodata/")
# temp = list.files(pattern="*.csv")
# for (i in 1:length(temp)){
#   fr = read.csv(temp[i], header = TRUE, stringsAsFactors = FALSE)
#   fr = na.omit(fr)
#   fr$end = fr$end %>% as.Date()
#   fr = aggregate(fr["load"], by=fr["end"], sum)
#   fr = fr[1:(length(fr$load)-1),]
#   fr[,paste0(temp[i])] = fr$load
#   df = left_join(df, fr, by=c("end"))
# }
# df = df[, -grep("load", colnames(df))]
# colnames(df) = c('end', 'Austria', 'Belgium', 'Switzerland', 'Germany', 'Denmark', 'Spain', 'France', 'UK', 'Ireland', 'Italy', 'Luxembourg', 'Netherlands', 'Norway', 'Portugal','Sweden')
# 
# 
# 
# # AUSTRALIA DATA
# 
# aus = read.csv("ausdata/VIC/PRICE_AND_DEMAND_201501_VIC1.csv", header =TRUE, stringsAsFactors = FALSE)
# aus$SETTLEMENTDATE = aus$SETTLEMENTDATE %>% as.Date()
# aus = aggregate(aus["TOTALDEMAND"], by=aus["SETTLEMENTDATE"], sum)
# aus = aus %>% filter(TOTALDEMAND > 10000)
# 
# temp = list.files("ausdata/VIC/",pattern="*.csv")
# for (i in 1:length(temp)){
#   ausx = read.csv(paste0("ausdata/VIC/",temp[i]), header = TRUE, stringsAsFactors = FALSE)
#   ausx$SETTLEMENTDATE = ausx$SETTLEMENTDATE %>% as.Date()
#   ausx = aggregate(ausx["TOTALDEMAND"], by=ausx["SETTLEMENTDATE"], sum)
#   ausx = ausx %>% filter(TOTALDEMAND >= 10000)
#   aus = rbind(aus, ausx)
# }
# 
# VIC = aus[!duplicated(aus), ]
# 
# aus = read.csv("ausdata/NSW/PRICE_AND_DEMAND_201501_NSW1.csv", header =TRUE, stringsAsFactors = FALSE)
# aus$SETTLEMENTDATE = aus$SETTLEMENTDATE %>% as.Date()
# aus = aggregate(aus["TOTALDEMAND"], by=aus["SETTLEMENTDATE"], sum)
# aus = aus %>% filter(TOTALDEMAND > 10000)
# 
# temp = list.files("ausdata/NSW/",pattern="*.csv")
# for (i in 1:length(temp)){
#   ausx = read.csv(paste0("ausdata/NSW/",temp[i]), header = TRUE, stringsAsFactors = FALSE)
#   ausx$SETTLEMENTDATE = ausx$SETTLEMENTDATE %>% as.Date()
#   ausx = aggregate(ausx["TOTALDEMAND"], by=ausx["SETTLEMENTDATE"], sum)
#   ausx = ausx %>% filter(TOTALDEMAND >= 10000)
#   aus = rbind(aus, ausx)
# }
# NSW = aus[!duplicated(aus), ]
# 
# 
# aus = read.csv("ausdata/QLD/PRICE_AND_DEMAND_201501_QLD1.csv", header =TRUE, stringsAsFactors = FALSE)
# aus$SETTLEMENTDATE = aus$SETTLEMENTDATE %>% as.Date()
# aus = aggregate(aus["TOTALDEMAND"], by=aus["SETTLEMENTDATE"], sum)
# aus = aus %>% filter(TOTALDEMAND > 10000)
# 
# temp = list.files("ausdata/QLD/",pattern="*.csv")
# for (i in 1:length(temp)){
#   ausx = read.csv(paste0("ausdata/QLD/",temp[i]), header = TRUE, stringsAsFactors = FALSE)
#   ausx$SETTLEMENTDATE = ausx$SETTLEMENTDATE %>% as.Date()
#   ausx = aggregate(ausx["TOTALDEMAND"], by=ausx["SETTLEMENTDATE"], sum)
#   ausx = ausx %>% filter(TOTALDEMAND >= 10000)
#   aus = rbind(aus, ausx)
# }
# QLD = aus[!duplicated(aus), ]
# 
# 
# aus = read.csv("ausdata/SA/PRICE_AND_DEMAND_201501_SA1.csv", header =TRUE, stringsAsFactors = FALSE)
# aus$SETTLEMENTDATE = aus$SETTLEMENTDATE %>% as.Date()
# aus = aggregate(aus["TOTALDEMAND"], by=aus["SETTLEMENTDATE"], sum)
# aus = aus %>% filter(TOTALDEMAND > 10000)
# 
# temp = list.files("ausdata/SA/",pattern="*.csv")
# for (i in 1:length(temp)){
#   ausx = read.csv(paste0("ausdata/SA/",temp[i]), header = TRUE, stringsAsFactors = FALSE)
#   ausx$SETTLEMENTDATE = ausx$SETTLEMENTDATE %>% as.Date()
#   ausx = aggregate(ausx["TOTALDEMAND"], by=ausx["SETTLEMENTDATE"], sum)
#   ausx = ausx %>% filter(TOTALDEMAND >= 10000)
#   aus = rbind(aus, ausx)
# }
# SA = aus[!duplicated(aus), ]
# 
# 
# aus = read.csv("ausdata/TAS/PRICE_AND_DEMAND_201501_TAS1.csv", header =TRUE, stringsAsFactors = FALSE)
# aus$SETTLEMENTDATE = aus$SETTLEMENTDATE %>% as.Date()
# aus = aggregate(aus["TOTALDEMAND"], by=aus["SETTLEMENTDATE"], sum)
# aus = aus %>% filter(TOTALDEMAND > 10000)
# 
# temp = list.files("ausdata/TAS/",pattern="*.csv")
# for (i in 1:length(temp)){
#   ausx = read.csv(paste0("ausdata/TAS/",temp[i]), header = TRUE, stringsAsFactors = FALSE)
#   ausx$SETTLEMENTDATE = ausx$SETTLEMENTDATE %>% as.Date()
#   ausx = aggregate(ausx["TOTALDEMAND"], by=ausx["SETTLEMENTDATE"], sum)
#   ausx = ausx %>% filter(TOTALDEMAND >= 10000)
#   aus = rbind(aus, ausx)
# }
# TAS = aus[!duplicated(aus), ]
# 
# remove(aus)
# aus = VIC
# aus$NSW = NSW$TOTALDEMAND
# aus$VIC = VIC$TOTALDEMAND
# aus$TAS = TAS$TOTALDEMAND
# aus$QLD = QLD$TOTALDEMAND
# aus$SA = SA$TOTALDEMAND
# 
# 
# aus = aus[, -grep("TOTALDEMAND", colnames(aus))]
# auswide = gather(aus, state, load, NSW:SA, factor_key=TRUE)
# auswide = auswide[order(auswide$SETTLEMENTDATE), ]
# #saving a state dataframe
# statewide = auswide
# 
# 
# # US DATA
# us = read.csv("usdata/EIA930_BALANCE_2015_Jul_Dec.csv", header =TRUE, stringsAsFactors = FALSE)
# us$Data.Date = us$Data.Date %>% as.Date(format = "%m/%d/%Y")
# us$Demand..MW.=  us$Demand..MW. %>% as.numeric()
# us = aggregate(Demand..MW. ~ Data.Date, data = us, sum)
# 
# temp = list.files("usdata/",pattern="*.csv")
# for (i in 1:length(temp)){
#   usx = read.csv(paste0("usdata/",temp[i]), header = TRUE, stringsAsFactors = FALSE)
#   usx$Data.Date = usx$Data.Date %>% as.Date(format = "%m/%d/%Y")
#   usx$Demand..MW.=  usx$Demand..MW. %>% as.numeric()
#   usx = aggregate(Demand..MW. ~ Data.Date, data = usx, sum)
#   us = rbind(us, usx)
# }
# US = us[!duplicated(us), ]
# US = US[order(US$Data.Date), ]
# colnames(US) = c("end","US")
# 
# # MASTER DATA FRAME
# worlddata = df[-17]
# auswide = aggregate(load ~ SETTLEMENTDATE, data = auswide, sum)
# auswide = auswide[(auswide$SETTLEMENTDATE> "2014-12-31" & auswide$SETTLEMENTDATE< "2020-08-01"),]
# worlddata = add_column(worlddata, Australia = auswide$load, .after = 1) #adds australia
# worlddata = left_join(worlddata, US, by=c("end")) # adds the US 
# 
# 
# write.csv(worlddata, 'worlddata.csv')
# worlddata = read.csv("worlddata.csv", header =TRUE, stringsAsFactors = FALSE)
# 
# worlddata = worlddata[-1]
# 
# worlddata = gather(worlddata, country, load, Australia:US, factor_key=TRUE)
# worlddata = worlddata[order(worlddata$end), ]
# 
# worlddata

```





```{r 2, echo=FALSE, cache=FALSE, fig.align='left', fig.height=4.5, fig.width=9, results='show'}

# data = worlddata

# country = c('Australia', 'Austria', 'Belgium', 'Switzerland', 'Germany', 'Denmark', 'Spain', 'France', 'UK', 'Ireland', 'Italy', 'Luxembourg', 'Netherlands', 'Norway', 'Portugal','Sweden','US')

# MAKE SARIMA DATA

# for (country_string in country){print(country_string)
#   # country_string = "US"
# data = worlddata
# data = data %>% filter(country == country_string)
# data[c("end","load")]
# data
# t20152018 = data[(data$end >= "2015-01-01" & data$end <= "2018-12-31"),]
# t20162019 = data[(data$end >= "2016-01-01" & data$end <= "2019-12-31"),]
# # t20152020 = data
# 
# 
# # Create a daily Date object - helps my work on dates
# inds <- seq(as.Date("2015-01-01"), as.Date("2018-12-31"), by = "day")
# 
# ## Create a time series object
# set.seed(25)
# myts = ts(t20152018$load,
#            start = c(2015, as.numeric(format(inds[1], "%j"))),
#            frequency = 7)
# 
# bestfit <- list(aicc=Inf)
# # Choose the best model by AICc
# for(i in 1:3) {
#   for (j in 1:3){
#     for (k in 1:3){
#     z1 <- fourier(ts(myts, frequency=7), K=i)
#     z2 <- fourier(ts(myts, frequency=365), K=j)
#     z3 <- fourier(ts(myts, frequency=30), K=k)
#     fit <- auto.arima(myts, xreg=cbind(z1, z2, z3), seasonal=F)
#     if(fit$aicc < bestfit$aicc) {
#       bestfit <- list(aicc=fit$aicc, i=i, j=j, k=k, fit=fit)
#     }
#     }
#   }
# }
# 
# # summary(bestfit$fit)
# fcBESTFIT2019 = forecast(bestfit$fit, xreg=cbind(
#                  fourier(ts(myts, frequency=7), K=bestfit$i, h=200),
#                  fourier(ts(myts, frequency=365), K=bestfit$j, h=200),
#                  fourier(ts(myts, frequency=30), K=bestfit$k, h=200)))
# 
# saveRDS(fcBESTFIT2019, file = paste0(country_string,"2019",".rds"))
# fcBESTFIT3 = readRDS(file = "ausdata/bf3.rds")
# # Create a daily Date object - helps my work on dates
# inds <- seq(as.Date("2016-01-01"), as.Date("2019-12-31"), by = "day")
# 
# ## Create a time series object
# set.seed(25)
# myts = ts(t20162019$load,
#            start = c(2019, as.numeric(format(inds[1], "%j"))),
#            frequency = 7)
# 
# bestfit <- list(aicc=Inf)
# # Choose the best model by AICc
# for(i in 1:3) {
#   for (j in 1:3){
#     for (k in 1:3){
#     z1 <- fourier(ts(myts, frequency=7), K=i)
#     z2 <- fourier(ts(myts, frequency=365), K=j)
#     z3 <- fourier(ts(myts, frequency=30), K=k)
#     fit <- auto.arima(myts, xreg=cbind(z1, z2, z3), seasonal=F)
#     if(fit$aicc < bestfit$aicc) {
#       bestfit <- list(aicc=fit$aicc, i=i, j=j, k=k, fit=fit)
#     }
#     }
#   }
# }
# 
# # summary(bestfit$fit)
# fcBESTFIT2020 = forecast(bestfit$fit, xreg=cbind(
#                  fourier(ts(myts, frequency=7), K=bestfit$i, h=200),
#                  fourier(ts(myts, frequency=365), K=bestfit$j, h=200),
#                  fourier(ts(myts, frequency=30), K=bestfit$k, h=200)))
# 
# saveRDS(fcBESTFIT2020, file = paste0(country_string,"2020",".rds"))
# }



```


<center> <h2>**SARIMAX**: Forecasting electricity consumption</h2> </center>

```{r , echo=FALSE, cache=FALSE, fig.align='left', fig.height=4.5, fig.width=9, results='show'}
# worlddata = gather(worlddata, country, load, Australia:US, factor_key=TRUE)
# worlddata = worlddata[order(worlddata$end), ]

country = c('Australia', 'Austria', 'Belgium', 'Switzerland', 'Germany', 'Denmark', 'Spain', 'France', 'UK', 'Ireland', 'Italy', 'Luxembourg', 'Netherlands', 'Norway', 'Portugal','Sweden','US')


worlddata = read.csv("worlddata.csv", header =TRUE, stringsAsFactors = FALSE)

worlddata = worlddata[-1]

worlddata = gather(worlddata, country, load, Australia:US, factor_key=TRUE)
worlddata = worlddata[order(worlddata$end), ]


worlddata$end = worlddata$end %>% as.Date()

addsarima = function(model,name){
x = seq(as.Date("2019-01-01"), as.Date("2019-07-19"), by = "day")
coun = rep(name,length(x))
model = data.frame(end = x, SARIMAX2019 = model$mean, country = coun)
model$country = model$country %>% as.factor()
worlddata = left_join(worlddata, model, by=c("end","country"))
return(worlddata)
}

Australia19 = readRDS(file = "SARIMAXdata/Australia2019.rds")
Austria19 = readRDS(file = "SARIMAXdata/Austria2019.rds")
Belgium19 = readRDS(file = "SARIMAXdata/Belgium2019.rds")
Switzerland19 = readRDS(file = "SARIMAXdata/Switzerland2019.rds")
Germany19 = readRDS(file = "SARIMAXdata/Germany2019.rds")
Denmark19 = readRDS(file = "SARIMAXdata/Denmark2019.rds")
Spain19 = readRDS(file = "SARIMAXdata/Spain2019.rds")
France19 = readRDS(file = "SARIMAXdata/France2019.rds")
UK19 = readRDS(file = "SARIMAXdata/UK2019.rds")
Ireland19 = readRDS(file = "SARIMAXdata/Ireland2019.rds")
Italy19 = readRDS(file = "SARIMAXdata/Italy2019.rds")
Luxembourg19 = readRDS(file = "SARIMAXdata/Luxembourg2019.rds")
Netherlands19 = readRDS(file = "SARIMAXdata/Netherlands2019.rds")
Norway19 = readRDS(file = "SARIMAXdata/Norway2019.rds")
Portugal19 = readRDS(file = "SARIMAXdata/Portugal2019.rds")
Sweden19 = readRDS(file = "SARIMAXdata/Sweden2019.rds")
worlddata$SARIMAX2019 = addsarima(Australia19,"Australia")$SARIMAX2019
worlddata = left_join(worlddata, addsarima(Austria19,"Austria"), by=c("end","country","load"))
worlddata$SARIMAX2019 = rowSums(worlddata[,c("SARIMAX2019.x", "SARIMAX2019.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:4)]
worlddata = left_join(worlddata, addsarima(Belgium19,"Belgium"), by=c("end","country","load"))
worlddata$SARIMAX2019 = rowSums(worlddata[,c("SARIMAX2019.x", "SARIMAX2019.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:4)]
worlddata = left_join(worlddata, addsarima(Switzerland19,"Switzerland"), by=c("end","country","load"))
worlddata$SARIMAX2019 = rowSums(worlddata[,c("SARIMAX2019.x", "SARIMAX2019.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:4)]
worlddata = left_join(worlddata, addsarima(Germany19,"Germany"), by=c("end","country","load"))
worlddata$SARIMAX2019 = rowSums(worlddata[,c("SARIMAX2019.x", "SARIMAX2019.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:4)]
worlddata = left_join(worlddata, addsarima(Denmark19,"Denmark"), by=c("end","country","load"))
worlddata$SARIMAX2019 = rowSums(worlddata[,c("SARIMAX2019.x", "SARIMAX2019.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:4)]
worlddata = left_join(worlddata, addsarima(Spain19,"Spain"), by=c("end","country","load"))
worlddata$SARIMAX2019 = rowSums(worlddata[,c("SARIMAX2019.x", "SARIMAX2019.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:4)]
worlddata = left_join(worlddata, addsarima(France19,"France"), by=c("end","country","load"))
worlddata$SARIMAX2019 = rowSums(worlddata[,c("SARIMAX2019.x", "SARIMAX2019.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:4)]
worlddata = left_join(worlddata, addsarima(UK19,"UK"), by=c("end","country","load"))
worlddata$SARIMAX2019 = rowSums(worlddata[,c("SARIMAX2019.x", "SARIMAX2019.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:4)]
worlddata = left_join(worlddata, addsarima(Ireland19,"Ireland"), by=c("end","country","load"))
worlddata$SARIMAX2019 = rowSums(worlddata[,c("SARIMAX2019.x", "SARIMAX2019.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:4)]
worlddata = left_join(worlddata, addsarima(Italy19,"Italy"), by=c("end","country","load"))
worlddata$SARIMAX2019 = rowSums(worlddata[,c("SARIMAX2019.x", "SARIMAX2019.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:4)]
worlddata = left_join(worlddata, addsarima(Luxembourg19,"Luxembourg"), by=c("end","country","load"))
worlddata$SARIMAX2019 = rowSums(worlddata[,c("SARIMAX2019.x", "SARIMAX2019.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:4)]
worlddata = left_join(worlddata, addsarima(Netherlands19,"Netherlands"), by=c("end","country","load"))
worlddata$SARIMAX2019 = rowSums(worlddata[,c("SARIMAX2019.x", "SARIMAX2019.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:4)]
worlddata = left_join(worlddata, addsarima(Norway19,"Norway"), by=c("end","country","load"))
worlddata$SARIMAX2019 = rowSums(worlddata[,c("SARIMAX2019.x", "SARIMAX2019.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:4)]
worlddata = left_join(worlddata, addsarima(Portugal19,"Portugal"), by=c("end","country","load"))
worlddata$SARIMAX2019 = rowSums(worlddata[,c("SARIMAX2019.x", "SARIMAX2019.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:4)]
worlddata = left_join(worlddata, addsarima(Sweden19,"Sweden"), by=c("end","country","load"))
worlddata$SARIMAX2019 = rowSums(worlddata[,c("SARIMAX2019.x", "SARIMAX2019.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:4)]

worlddata[(worlddata$SARIMAX2019 == 0),]$SARIMAX2019 <- NA


addsarima = function(model,name){
x = seq(as.Date("2020-01-01"), as.Date("2020-07-18"), by = "day")
coun = rep(name,length(x))
model = data.frame(end = x, SARIMAX2020 = model$mean, country = coun)
model$country = model$country %>% as.factor()
worlddata = left_join(worlddata, model, by=c("end","country"))
return(worlddata)
}

Australia20 = readRDS(file = "SARIMAXdata/Australia2020.rds")
Austria20 = readRDS(file = "SARIMAXdata/Austria2020.rds")
Belgium20 = readRDS(file = "SARIMAXdata/Belgium2020.rds")
Switzerland20 = readRDS(file = "SARIMAXdata/Switzerland2020.rds")
Germany20 = readRDS(file = "SARIMAXdata/Germany2020.rds")
Denmark20 = readRDS(file = "SARIMAXdata/Denmark2020.rds")
Spain20 = readRDS(file = "SARIMAXdata/Spain2020.rds")
France20 = readRDS(file = "SARIMAXdata/France2020.rds")
UK20 = readRDS(file = "SARIMAXdata/UK2020.rds")
Ireland20 = readRDS(file = "SARIMAXdata/Ireland2020.rds")
Italy20 = readRDS(file = "SARIMAXdata/Italy2020.rds")
Luxembourg20 = readRDS(file = "SARIMAXdata/Luxembourg2020.rds")
Netherlands20 = readRDS(file = "SARIMAXdata/Netherlands2020.rds")
Norway20 = readRDS(file = "SARIMAXdata/Norway2020.rds")
Portugal20 = readRDS(file = "SARIMAXdata/Portugal2020.rds")
Sweden20 = readRDS(file = "SARIMAXdata/Sweden2020.rds")
worlddata$SARIMAX2020 = addsarima(Australia20,"Australia")$SARIMAX2020
worlddata = left_join(worlddata, addsarima(Austria20,"Austria"), by=c("end","country","load","SARIMAX2019"))
worlddata$SARIMAX2020 = rowSums(worlddata[,c("SARIMAX2020.x", "SARIMAX2020.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:5)]
worlddata = left_join(worlddata, addsarima(Belgium20,"Belgium"), by=c("end","country","load","SARIMAX2019"))
worlddata$SARIMAX2020 = rowSums(worlddata[,c("SARIMAX2020.x", "SARIMAX2020.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:5)]
worlddata = left_join(worlddata, addsarima(Switzerland20,"Switzerland"), by=c("end","country","load","SARIMAX2019"))
worlddata$SARIMAX2020 = rowSums(worlddata[,c("SARIMAX2020.x", "SARIMAX2020.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:5)]
worlddata = left_join(worlddata, addsarima(Germany20,"Germany"), by=c("end","country","load","SARIMAX2019"))
worlddata$SARIMAX2020 = rowSums(worlddata[,c("SARIMAX2020.x", "SARIMAX2020.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:5)]
worlddata = left_join(worlddata, addsarima(Denmark20,"Denmark"), by=c("end","country","load","SARIMAX2019"))
worlddata$SARIMAX2020 = rowSums(worlddata[,c("SARIMAX2020.x", "SARIMAX2020.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:5)]
worlddata = left_join(worlddata, addsarima(Spain20,"Spain"), by=c("end","country","load","SARIMAX2019"))
worlddata$SARIMAX2020 = rowSums(worlddata[,c("SARIMAX2020.x", "SARIMAX2020.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:5)]
worlddata = left_join(worlddata, addsarima(France20,"France"), by=c("end","country","load","SARIMAX2019"))
worlddata$SARIMAX2020 = rowSums(worlddata[,c("SARIMAX2020.x", "SARIMAX2020.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:5)]
worlddata = left_join(worlddata, addsarima(UK20,"UK"), by=c("end","country","load","SARIMAX2019"))
worlddata$SARIMAX2020 = rowSums(worlddata[,c("SARIMAX2020.x", "SARIMAX2020.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:5)]
worlddata = left_join(worlddata, addsarima(Ireland20,"Ireland"), by=c("end","country","load","SARIMAX2019"))
worlddata$SARIMAX2020 = rowSums(worlddata[,c("SARIMAX2020.x", "SARIMAX2020.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:5)]
worlddata = left_join(worlddata, addsarima(Italy20,"Italy"), by=c("end","country","load","SARIMAX2019"))
worlddata$SARIMAX2020 = rowSums(worlddata[,c("SARIMAX2020.x", "SARIMAX2020.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:5)]
worlddata = left_join(worlddata, addsarima(Luxembourg20,"Luxembourg"), by=c("end","country","load","SARIMAX2019"))
worlddata$SARIMAX2020 = rowSums(worlddata[,c("SARIMAX2020.x", "SARIMAX2020.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:5)]
worlddata = left_join(worlddata, addsarima(Netherlands20,"Netherlands"), by=c("end","country","load","SARIMAX2019"))
worlddata$SARIMAX2020 = rowSums(worlddata[,c("SARIMAX2020.x", "SARIMAX2020.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:5)]
worlddata = left_join(worlddata, addsarima(Norway20,"Norway"), by=c("end","country","load","SARIMAX2019"))
worlddata$SARIMAX2020 = rowSums(worlddata[,c("SARIMAX2020.x", "SARIMAX2020.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:5)]
worlddata = left_join(worlddata, addsarima(Portugal20,"Portugal"), by=c("end","country","load","SARIMAX2019"))
worlddata$SARIMAX2020 = rowSums(worlddata[,c("SARIMAX2020.x", "SARIMAX2020.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:5)]
worlddata = left_join(worlddata, addsarima(Sweden20,"Sweden"), by=c("end","country","load","SARIMAX2019"))
worlddata$SARIMAX2020 = rowSums(worlddata[,c("SARIMAX2020.x", "SARIMAX2020.y")], na.rm=TRUE)
worlddata = worlddata[,c(1:5)]

worlddata[(worlddata$SARIMAX2020 == 0),]$SARIMAX2020 <- NA

# worlddata[(worlddata$end >= "2020-01-01"),]

```



```{r, echo=FALSE, cache=FALSE, fig.align='left', fig.height=4.5, fig.width=9, results='show'}

country = c('Australia', 'Austria', 'Belgium', 'Switzerland', 'Germany', 'Denmark', 'Spain', 'France', 'UK', 'Ireland', 'Italy', 'Luxembourg', 'Netherlands', 'Norway', 'Portugal','Sweden','US')


button_list <- lapply(1:length(country), function(x){
  list(method = "restyle",
       args = list("transforms[0].value", country[x]),
       label = country[x])
})



p <- plot_ly(data = worlddata, x = ~end, y = ~load, type = 'scatter', text = ~end, hoverinfo =~as.factor(end),
             mode = 'lines', alpha = 1, line = list(color = '#06d6a0'), name = paste0("Selected Country"),
             transforms = list( list(
                            type = 'filter',
                            target = ~country,
                            operation = '=',
                            value = unique(worlddata$country)[1]
      ))) %>% layout(
        title = paste0('SARIMAX on Energy Consumption'),
         xaxis = list(title = 'Date'),
         yaxis = list(title = 'MW of Energy'),
    updatemenus = list(
      list(
  xanchor = 'left',
  yanchor = "top",
  pad = list('r'= 0, 't'= 10, 'b' = 10),
  x = 0,
  y = 1.27,
        type = 'dropdown',
        active = 0,
        buttons = button_list
        )
      )
    )
  
# p <- plotly_build(p)


p = p %>% layout(xaxis = list(
        range =
            c(as.numeric(as.POSIXct("2018-11-01", format="%Y-%m-%d"))*1000,
              as.numeric(as.POSIXct("2020-06-30", format="%Y-%m-%d"))*1000),
        type = "date")) 

p = p  %>% layout(xaxis = list(rangeslider = list(type = "date")))

p = p  %>% add_trace(data = worlddata, x = ~end, y = ~SARIMAX2019, type = 'scatter',line=list(color='#e63946',dash='dashed'),
             mode = 'lines', name = 'SARIMAX 2019', alpha = 1)
p = p  %>% add_trace(data = worlddata, x = ~end, y = ~SARIMAX2020, type = 'scatter',line=list(color='#457b9d',dash='dashed'),
             mode = 'lines', name = 'SARIMAX 2020', alpha = 1)
p

# saveRDS(p, file = "worldtime.rds")
# worldtime = readRDS(file = "worldtime.rds")

```

The figure above is a time-series of electricity consumption in each country. with an overlay of a SARIMAX model predicting energy consumption in 2019 vs 2020, having been trained on the previous 4 years worth of data. The appendix outlines the accuracy of these models.The objective of this plot and table is to illustrate the predictability of electricity consumption data during a normal year vs a pandemic enduced year. The change is clearly picked up in the drastic changes in accuracy.

Electricity consumption can be attributed to weather, seasonality, business cycles & base load. Weather and seasonality are present moment indicators unless a weather forecast can be added to the model. The temperature causes one to use heating and cooling measures. Business cycles and base load (level of business activity) can be presumptiously reactive to conditions unlike weather and seasonality which are reactive in the moment. Hence, electricity consumption attributed to business cycles and base load can be a forward looking indicator into economic activity. 



<center> <h2>**Anomalous Behaviours**: An experimental approach to detect change in production activity</h2> </center>


t-SNE (t-distributed Stochastic Neighbor Embedding) is something called nonlinear dimensionality reduction. This is an algorithm which allows us to separate data that cannot be separated by any straight line. Illustrated below are 3 years worth of Electricity Demand Data from Victoria. 2018 in red, 2019 in blue & 2020 in orange. Hovering over the data, we are able to see what factors such as RRP of electricity, week, day & hour impact the cluster formed. Points which appear further away are indicative of outliers. Interestingly, March 2020 appears to be the only occurance where the pattern breaks.  


```{r , echo=FALSE, fig.align='left', fig.height=4.5, fig.width=9, results='show'}

aus = read.csv("ausdata/VIC/PRICE_AND_DEMAND_201801_VIC1.csv", header =TRUE, stringsAsFactors = FALSE)
temp = list.files("ausdata/VIC/",pattern="*.csv")
for (i in 1:length(temp)){
  ausx = read.csv(paste0("ausdata/VIC/",temp[i]), header = TRUE, stringsAsFactors = FALSE)
  aus = rbind(aus, ausx)
}
aus = aus[c(-1,-5)]
aus$SETTLEMENTDATE = as.POSIXct(aus$SETTLEMENTDATE, format="%Y/%m/%d %H:%M:%S")
aus$SETTLEMENTDATE   = strftime(aus$SETTLEMENTDATE, "%Y:%m:%d %H:00:00") %>% as.character() %>% as.POSIXct(format="%Y:%m:%d %H:%M:%S")

```



```{r , echo=FALSE, fig.align='left', fig.height=4.5, fig.width=9, results='show'}

monthdata = function(data,sdate,edata){
  temp = subset(data, SETTLEMENTDATE >= sdate & SETTLEMENTDATE <= edata)
  temp2 = aggregate(RRP~SETTLEMENTDATE,data=temp,sum)
  sub = aggregate(TOTALDEMAND~SETTLEMENTDATE,data=temp,sum)
  sub$RRP = temp2$RRP
  sub$week  = strftime(sub$SETTLEMENTDATE  ,"%V")
  sub$day  = strftime(sub$SETTLEMENTDATE, "%u")
  sub$hour  = strftime(sub$SETTLEMENTDATE, "%H")
  sub = unique(sub)
  cols <- c("week", "day", "hour")
  sub[cols] <- lapply(sub[cols], factor)
  sub$TOTALDEMAND = sub$TOTALDEMAND %>% as.numeric()
  sub$RRP = sub$RRP %>% as.numeric()
  set.seed(42)
  tsne <- Rtsne(sub[-1], check_duplicates = FALSE, pca = TRUE, perplexity=50, theta=0.0, dims=2)
  
  sub = c(tsne$Y %>% as.data.frame(), sub)
  return(sub)
}

```


```{r , echo=FALSE, fig.align='left', fig.height=4.5, fig.width=9, results='show'}

plotmonth = function(aus,num_month,end,month){
  set.seed(42)
  a <- list(
  text = month,
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = 1,
  showarrow = FALSE
  )
  
  
  mon2018 = monthdata(aus,sprintf("2018-%s-01",num_month),sprintf("2018-%s-%s",num_month,end))
  mon2019 = monthdata(aus,sprintf("2019-%s-01",num_month),sprintf("2019-%s-%s",num_month,end))
  mon2020 = monthdata(aus,sprintf("2020-%s-01",num_month),sprintf("2020-%s-%s",num_month,end))
  
  mon = c(mon2018, mon2019, mon2020) %>% as.data.frame()
  
  plot_ly( ) %>% 
      add_trace(data = mon, x = ~V1, y = ~V2, type = 'scatter', mode = 'markers', name = '2018', 
                text = ~paste(SETTLEMENTDATE,'</br></br>','TOTAL DEMAND', TOTALDEMAND,'</br>',
                              'RRP: $',RRP,'</br>', 'WEEK', week, '</br>', 'DAY',day,'</br>',
                              'HOUR', hour, '</br>'),
                marker = list(size = ~TOTALDEMAND, sizeref = 4000, sizemode = 'area', color = 'red', line = list(color = 'red'))) %>%
   add_trace(data = mon, x = ~V1.1, y = ~V2.1, type = 'scatter', mode = 'markers', name = '2019', 
                text = ~paste(SETTLEMENTDATE.1,'</br></br>','TOTAL DEMAND', TOTALDEMAND.1,'</br>',
                              'RRP: $',RRP.1,'</br>', 'WEEK', week.1, '</br>', 'DAY',day.1,'</br>',
                              'HOUR', hour.1, '</br>'),
                marker = list(size = ~TOTALDEMAND.1, sizeref = 4000, sizemode = 'area', color = 'blue', line = list(color = 'blue'))) %>%
   add_trace(data = mon, x = ~V1.2, y = ~V2.2, type = 'scatter', mode = 'markers', name = '2020', 
                text = ~paste(SETTLEMENTDATE.2,'</br></br>','TOTAL DEMAND', TOTALDEMAND.2,'</br>',
                              'RRP: $',RRP.2,'</br>', 'WEEK', week.2, '</br>', 'DAY',day.2,'</br>',
                              'HOUR', hour.2, '</br>'),
                marker = list(size = ~TOTALDEMAND.2, sizeref = 4000, sizemode = 'area', color = 'orange', line = list(color = 'orange')))%>% layout(annotations = a)
  # %>% layout(title = month)
}
```


<center> <h3>Monthly Electricity Consumption Patterns in Victoria using t-SNE</h3> </center>
```{r , echo=FALSE, fig.align='left', fig.height=9, fig.width=9, results='show'}

# jan = plotmonth(aus,01,31,'JAN') 
# feb = plotmonth(aus,02,28,'FEB')
# mar = plotmonth(aus,03,31,'MAR')
# apr = plotmonth(aus,04,30,'APR')
# may = plotmonth(aus,05,31,'MAY')
# jun = plotmonth(aus,06,30,'JUN')
# jul = plotmonth(aus,07,31,'JUL')
# aug = plotmonth(aus,08,31,'AUG')
# 
# tsneplot = subplot(jan,feb,mar,apr,may,jun,jul,aug,nrows=4)  %>% layout(showlegend = FALSE)
# saveRDS(tsneplot, file = "tsneplot.rds")


tsneplot= readRDS(file = "tsneplot.rds")
tsneplot

#     add_annotations(
#         text = "MONTHLY ELECTRICITY CONSUMPTION PATTERNS IN VICTORIA",
#         x = 0.5,
#         y = 0,
#         yref = "paper",
#         xref = "paper",
#         xanchor = "center",
#         yanchor = "bottom",
#         yshift = 415,
#         showarrow = FALSE,
#         font = list(size = 15)
#     ) 

```



<center> <h3>Benfords law on Electricity Load 2020 VS 2019 In Western Europe</h3> </center>
```{r, echo=FALSE, cache=FALSE, fig.align='left', fig.height=4.5, fig.width=9, results='show'}



# WESTERN EURO DATA HOUR

fr = read.csv("eurodata/fr.csv", header =TRUE, stringsAsFactors = FALSE)
fr = na.omit(fr)
fr$hour = substr(fr$end,11,nchar(fr$end)-12)
fr$year = substr(fr$end,1,nchar(fr$end)-21)
fr  = aggregate(load ~ hour + year, data = fr, mean)
df = fr
setwd("eurodata/")
temp = list.files(pattern="*.csv")
for (i in 1:length(temp)){
  fr = read.csv(temp[i], header =TRUE, stringsAsFactors = FALSE)
  fr = na.omit(fr)
  fr$hour = substr(fr$end,11,nchar(fr$end)-12)
  fr$year = substr(fr$end,1,nchar(fr$end)-21)
  fr  = aggregate(load ~ hour + year, data = fr, mean)
  fr[,paste0(temp[i])] = fr$load
  df = left_join(df, fr, by=c("hour","year"))
}
df = df[, -grep("load", colnames(df))]
colnames(df) = c('hour','year', 'Austria', 'Belgium', 'Switzerland', 'Germany', 'Denmark', 'Spain', 'France', 'UK', 'Ireland', 'Italy', 'Luxembourg', 'Netherlands', 'Norway', 'Portugal','Sweden')

eurohourwide = gather(df, country, load, Austria:Sweden, factor_key=TRUE)
eurohourwide = eurohourwide[-3]

country = c('Austria', 'Belgium', 'Switzerland', 'Germany', 'Denmark', 'Spain', 'France', 'UK', 'Ireland', 'Italy', 'Luxembourg', 'Netherlands', 'Norway', 'Portugal','Sweden')

eurohourwide <- eurohourwide[order(eurohourwide$year), ]


euro2020 = eurohourwide %>% filter(year == 2020)
euro2019 = eurohourwide %>% filter(year == 2019)

# eurodiff$load = euro2020$load - euro2019$load

trends2020 = benford(euro2020$load, number.of.digits = 1, discrete = T, sign = "positive")
trends2019 = benford(euro2019$load, number.of.digits = 1, discrete = T, sign = "positive")
# trendsdiff = benford(eurodiff$load, number.of.digits = 1, discrete = T, sign = "positive")


trends2020$data = trends2020$data %>% mutate(bl=recode(data.digits,
                         `1`=30.1,`2`= 17.6,`3`= 12.5,`4`= 9.7,`5`= 7.9,`6`= 6.7,`7`= 5.8,`8`= 5.1,`9`= 4.6,))

trends2019$data = trends2019$data %>% mutate(bl=recode(data.digits,
                         `1`=30.1,`2`= 17.6,`3`= 12.5,`4`= 9.7,`5`= 7.9,`6`= 6.7,`7`= 5.8,`8`= 5.1,`9`= 4.6,))

trends2020$s.o.data = trends2020$s.o.data %>% mutate(bl=recode(data.second.order.digits,
                         `1`=30.1,`2`= 17.6,`3`= 12.5,`4`= 9.7,`5`= 7.9,`6`= 6.7,`7`= 5.8,`8`= 5.1,`9`= 4.6,))
trends2019$s.o.data = trends2019$s.o.data %>% mutate(bl=recode(data.second.order.digits,
                         `1`=30.1,`2`= 17.6,`3`= 12.5,`4`= 9.7,`5`= 7.9,`6`= 6.7,`7`= 5.8,`8`= 5.1,`9`= 4.6,))


gg1 = ggplot(trends2020$data,aes(x = data.digits, fill = data.digits)) +
  geom_bar(position = "identity", fill = "#90e0ef") +
  theme_minimal() + xlab("First Digit")+ geom_line(aes(x = data.digits, y = bl*3),inherit.aes = FALSE, size = 1, color="black", alpha = 0.5, group = 1) +
  scale_y_continuous(sec.axis = sec_axis(~. /3))
# + labs(title="Benfords Law")


gg2 = ggplot(trends2020$s.o.data,aes(x = data.second.order.digits, fill = data.second.order.digits)) +
  geom_bar(position = "identity", fill = "#90e0ef") +
  theme_minimal() + xlab("Second Order First Digit") + geom_line(aes(x = data.second.order.digits, y = bl*3),inherit.aes = FALSE, size = 1, color="black", alpha = 0.5, group = 1) +
  scale_y_continuous(sec.axis = sec_axis(~. /3))#+ labs(title="Second Order Benfords Law")



gg3 = ggplot(trends2019$data,aes(x = data.digits, fill = data.digits)) +
  geom_bar(position = "identity", fill = "#ade8f4") +
  theme_minimal() + xlab("First Digit")+ geom_line(aes(x = data.digits, y = bl*3),inherit.aes = FALSE, size = 1, color="black", alpha = 0.5, group = 1) +
  scale_y_continuous(sec.axis = sec_axis(~. /3))


gg4 = ggplot(trends2019$s.o.data,aes(x = data.second.order.digits, fill = data.second.order.digits)) +
  geom_bar(position = "identity", fill = "#ade8f4") +
  theme_minimal() + xlab("Second Order First Digit")+ geom_line(aes(x = data.second.order.digits, y = bl*3),inherit.aes = FALSE, size = 1, color="black", alpha = 0.5, group = 1) +
  scale_y_continuous(sec.axis = sec_axis(~. /3))



a <- list(
  text = "2020 First Order Benfords Law",
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = 1,
  showarrow = FALSE
)

b <- list(
  text = "2020 Second Order Benfords Law",
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = 1,
  showarrow = FALSE
)

c <- list(
  text = "2019 First Order Benfords Law",
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = 1,
  showarrow = FALSE
)

d <- list(
  text = "2019 Second Order Benfords Law",
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = 1,
  showarrow = FALSE
)
ay <- list(
  overlaying = "y",
  side = "right",
  title = "Ideal Benfords Law"
)


subplot(ggplotly(gg1)%>%layout(annotations = a),
        ggplotly(gg2)%>%layout(annotations = b),
        ggplotly(gg3)%>%layout(annotations = c),
        ggplotly(gg4)%>%layout(annotations = d),
        nrows = 2,shareY = TRUE)%>% layout(showlegend = F, yaxis = list(anchor = 'x1'),
            yaxis2 = list(showticklabels = T), yaxis4 = list(showticklabels = F),
            xaxis = list(showticklabels = F), xaxis2 = list(showticklabels = F)) %>%
    add_annotations(
        text = "First Digit in Hourly Load",
        x = 0.5,
        y = 0,
        yref = "paper",
        xref = "paper",
        xanchor = "center",
        yanchor = "bottom",
        yshift = -35,
        showarrow = FALSE,
        font = list(size = 15)
    )
# %>% layout(title= "Benfords Law")

# ggplotly(gg)



# ggplotly(plot(trends))

# trends2020$data = trends2020$data %>% mutate(bl=recode(data.digits, 
#                          `1`=30.1,`2`= 17.6,`3`= 12.5,`4`= 9.7,`5`= 7.9,`6`= 6.7,`7`= 5.8,`8`= 5.1,`9`= 4.6,))
# 
# # euro2020 = eurohourwide %>% filter(year == 2020) %>% select(load)
# gg1 + geom_line(aes(x = data.digits, y = bl*3),inherit.aes = FALSE, size = 1.5, color="black", alpha = 0.5, group = 1) + 
#   scale_y_continuous(sec.axis = sec_axis(~. /3))

```