---
title: <center><h1>Can electricity consumption patterns tell us anything about the pandemic?</h1></center>
author: 
output:
  html_document: 
    toc: false
    theme: flatly
    toc_float: true
    collapsed: true
    number_sections: false
    toc_depth: 1
editor_options: 
  chunk_output_type: inline
---

<center>
*This report explores electricity consumption patterns within forecasting, demand and behaviours to investigate if data can show us actionable insights.*
</center><br> <!-- New line --> 

1. **Policy Impact**: *Exploring the seasonally adjusted difference between 2020 & 2019 electricity consumption*

2. **Demand & Economics**: *Duck curve & the economy - an analysis into electricity consumption*

3. **Production Function**: *An experimental approach to detect patterns in electricity demand*


<center> <h2> **Policy Impact**: Exploring the seasonally adjusted difference between 2020 & 2019 electricity consumption</h2> </center>

Let’s begin with a look at the day to day differences between 2020 and 2019 across the world adjusted for seasonality. Exploring the COVID-19 responses across the world, it is evident that difference in electricity consumption is drastically impacted based on the economic policies that have been put in place in each country. For example, Italy who began nation-wide lockdowns on March 9th, saw an immediate drop in electricity consumption over the next few days. On March 22nd all factories were closed, and all nonessential production was halted, causing a further dip in consumption difference. This same story can be told with several other countries. Interestingly, Sweden who chose a mitigation strategy showed very little difference compared to its Scandinavian neighbours Norway and Denmark, who took much more preventative measures. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
library(ggplot2)
library(tidyverse)
library(gridExtra)
library(dplyr)
library(plotly)
library(itertools)
library(scales)
library(forecast)
library(Rtsne)
library(RColorBrewer)
library(zoo)
```


```{r , echo=FALSE, fig.align='left', fig.height=4.5, fig.width=9, results='show'}
worlddata = read.csv("worlddata.csv", header =TRUE, stringsAsFactors = FALSE)
worlddata = worlddata[-1]
worlddata = gather(worlddata, country, load, Australia:US, factor_key=TRUE)
# worlddata = worlddata[order(worlddata$end), ]

worlddata2019 = worlddata[(worlddata$end >= "2019-01-01	" & worlddata$end <= "2019-08-31"),]
worlddata2020 = worlddata[(worlddata$end >= "2020-01-01	" & worlddata$end <= "2020-08-31"),]

worlddata2019$week  = strftime(worlddata2019$end ,"%V")
worlddata2019$day  = strftime(worlddata2019$end, "%u")
worlddata2020$week  = strftime(worlddata2020$end ,"%V")
worlddata2020$day  = strftime(worlddata2020$end, "%u")

worlddatadiff = merge(worlddata2019, worlddata2020, by=c("week","day","country"))
worlddatadiff$diff = (worlddatadiff$load.y / worlddatadiff$load.x)*100 -100
worlddatadiff[worlddatadiff == Inf] <- NA

p <- plot_ly() %>%
  add_trace( data = worlddatadiff, x = ~end.y, y = ~diff, type = 'scatter',
             mode = 'lines', color = ~as.factor(country), alpha = 0.7)
p <- plotly_build(p)

legendItems <- list(Australia = 'legendonly', Austria = 'legendonly', Belgium= 'legendonly', Switzerland= 'legendonly', Germany= 'legendonly', Denmark= 'legendonly', Spain= 'legendonly', France= 'legendonly', UK= 'legendonly', Ireland= 'legendonly', Italy= T, Luxembourg= 'legendonly', Netherlands= 'legendonly', Norway= 'legendonly', Portugal= 'legendonly', Sweden= T, US = 'legendonly')

for(i in seq_along(p$x$data)){
  p$x$data[[i]]$visible <- legendItems[[p$x$data[[i]]$name]]
}

p = p %>% layout(title = 'Energy Consumption Change (%) 2020-2019 Adjusted for Seasonality',
         xaxis = list(title = 'Date'),
         yaxis = list(title = 'Change (%)'))

p = p %>%
    layout(xaxis = list(
        range =
            c(as.numeric(as.POSIXct("2020-01-01", format="%Y-%m-%d"))*1000,
              as.numeric(as.POSIXct("2020-07-30", format="%Y-%m-%d"))*1000),
        type = "date"))

p

```

*Note: See the references page for data sources & data representation of Australia & US* 





```{r fig.cap="Figure 1: Descriptive Plots" , echo=FALSE, fig.align='left', fig.height=9, fig.width=26, results='hide'}

# fr = read.csv("eurodata/fr.csv", header =TRUE, stringsAsFactors = FALSE)
# fr$end = fr$end %>% as.Date()
# fr = aggregate(fr["load"], by=fr["end"], sum)
# fr = fr[1:(length(fr$load)-1),]
# fr = fr[(fr$end> "2018-01-01	" & fr$end < "2020-07-30"),]
# df = fr
# setwd("eurodata/")
# temp = list.files(pattern="*.csv")
# for (i in 1:length(temp)){
#   fr = read.csv(temp[i], header = TRUE, stringsAsFactors = FALSE)
#   fr = na.omit(fr)
#   fr$end = fr$end %>% as.Date()
#   fr = aggregate(fr["load"], by=fr["end"], sum)
#   fr = fr[1:(length(fr$load)-1),]
#   fr = fr[(fr$end> "2018-01-01	" & fr$end < "2020-07-30"),]
#   fr[,paste0(temp[i])] = fr$load
#   df = left_join(df, fr, by=c("end"))
# }
# df = df[, -grep("load", colnames(df))]
# colnames(df) = c('end', 'Austria', 'Belgium', 'Switzerland', 'Germany', 'Denmark', 'Spain', 'France', 'UK', 'Ireland', 'Italy', 'Luxembourg', 'Netherlands', 'Norway', 'Portugal','Sweden')
# 
# dfwide = gather(df, country, load, Austria:Sweden, factor_key=TRUE)
# 
# write.csv(dfwide, 'widedata.csv')
# dfwide = read.csv("widedata.csv", header =TRUE, stringsAsFactors = FALSE)
# dfwide = dfwide[-1]
```



```{r fig.cap="Figure 1: Descriptive Plots" , echo=FALSE, fig.align='left', fig.height=4.5, fig.width=9, results='show'}

# p <- plot_ly() %>%
#   add_trace( data = dfwide, x = ~end, y = ~load, type = 'scatter', 
#              mode = 'lines', color = ~as.factor(country))
# p <- plotly_build(p)
# 
# legendItems <- list(Austria = 'legendonly', Belgium= 'legendonly', Switzerland= 'legendonly', Germany= 'legendonly', Denmark= 'legendonly', Spain= 'legendonly', France= TRUE, UK= 'legendonly', Ireland= 'legendonly', Italy= TRUE, Luxembourg= 'legendonly', Netherlands= 'legendonly', Norway= 'legendonly', Portugal= 'legendonly', Sweden= 'legendonly')
# 
# for(i in seq_along(p$x$data)){
#   p$x$data[[i]]$visible <- legendItems[[p$x$data[[i]]$name]]
# }
# 
# #### LONG FORMAT DATA 
# # fig = plot_ly(df, x = ~end, y = ~Spain, name = "Spain", type = 'scatter', mode = 'lines', colors = "red") 
# # xy.list <- as.list(as.data.frame((df)))
# # for(i in colnames(df)[-1]) { fig <- add_trace(fig, y=xy.list[[i]], x=xy.list[['end']], 
# #                                               name = paste0(i),  type = 'scatter', 
# #                                               mode = 'lines',evaluate = TRUE) }
# 
# p = p %>% layout(title = 'Energy Consumption in Western Europe',
#          xaxis = list(title = 'Time'),
#          yaxis = list(title = 'Energy Consumption (MW)'))
# 
# p = p %>%
#     layout(xaxis = list(
#         range = 
#             c(as.numeric(as.POSIXct("2018-00-01", format="%Y-%m-%d"))*1000,
#               as.numeric(as.POSIXct("2020-07-30", format="%Y-%m-%d"))*1000),
#         type = "date"))
# 
# p

```




```{r fig.cap="Figure 2: Descriptive Plots" , echo=FALSE, fig.align='left', fig.height=9, fig.width=26, results='show'}
# fr = read.csv("eurodata/fr.csv", header =TRUE, stringsAsFactors = FALSE)
# fr = na.omit(fr)
# fr$end = fr$end %>% as.Date()
# fr = aggregate(fr["load"], by=fr["end"], sum)
# fr = fr[1:(length(fr$load)-1),]
# TRAIN2015TO2018 = fr[(fr$end> "2015-01-01	" & fr$end < "2018-12-31"),]
# TEST2017 = fr[(fr$end> "2017-01-01" & fr$end < "2017-07-30"),]
# TEST2018 = fr[(fr$end> "2018-01-01" & fr$end < "2018-07-30"),]
# TEST2019 = fr[(fr$end> "2019-01-01" & fr$end < "2019-07-30"),]
# TRAIN2016TO2019 = fr[(fr$end> "2016-01-01	" & fr$end < "2019-12-31"),]
# TEST2020 = fr[(fr$end> "2020-01-01" & fr$end < "2020-07-30"),]
# 
# x1 = ggplot(fr, aes(x=end, y=load, color = "Electricity Consumed")) +
#   geom_line(size = 2) + theme_minimal() +
#   xlab("Date") + ylab("MW of Electricity Consumed") + scale_x_date(date_labels = "%Y") + ggtitle("FRANCE ELECTRICITY CONSUMPTION")
# 
# fcBESTFIT1 = readRDS(file = "eurodata/bf1.rds")
# fcBESTFIT2 = readRDS(file = "eurodata/bf2.rds")
# p = readRDS(file = "eurodata/p.rds")
# q = readRDS(file = "eurodata/q.rds")

# lay <- rbind(c(1,1,1,1),
#              c(2,2,3,3))
# 
# grid.arrange(x1, p, q, layout_matrix = lay)

# a <- list(
#   text = "TRAINING ON 2015 TO 2018 AND TESTING ON THE FIRST 209 DAYS OF 2019 - FRANCE ELECTRICITY CONSUMPTION",
#   xref = "paper",
#   yref = "paper",
#   yanchor = "bottom",
#   xanchor = "center",
#   align = "center",
#   x = 0.5,
#   y = 1,
#   showarrow = FALSE
# )
# 
# b <- list(
#   text = "TRAINING ON 2016 TO 2019 AND TESTING ON THE FIRST 209 DAYS OF 2020 - FRANCE ELECTRICITY CONSUMPTION
# ",
#   xref = "paper",
#   yref = "paper",
#   yanchor = "bottom",
#   xanchor = "center",
#   align = "center",
#   x = 0.5,
#   y = 1,
#   showarrow = FALSE
# )
# 
# 
# subplot(ggplotly(p)%>%layout(annotations = a), 
#         ggplotly(q)%>%layout(annotations = b), shareY = TRUE)

```





<center> <h2>**Demand & Economics**: Duck curve & the economy - an analysis into electricity consumption</h2> </center>

With the rise in solar energy production, anticipation of electricity demand has been at the forefront of utility companies’ priorities. The duck curve refers to the demand for electricity at any given time during the day. The early mornings consist of low energy demands, but as people wake up and businesses begin production, demand rises. This peaks around sunset before dropping. As you may have guessed, the production of energy during the peak hours of the day helps reduce the demand needed. This is evident as the year goes on. The dip during mid-day drops lower and lower, forming a duck like shape. This is more prominent in countries with renewable energy rebates such as Sweden’s tax regulation mechanisms and subsidy scheme.

There are two critical issues that arise from this. Firstly, as steeper drops in demand occur, more rapid increases in production are needed during peak hours with no sunlight. This poses a serious burden on power infrastructure and diminishes efficiency. The second issue is that during days of over production in solar energy, grid managers turn off solar panels to prevent overloading the power grid, discarding extra solar energy.

Evolutions in battery technology provide a potential solution for this. As battery technology continues to evolve, we are able to store energy more efficiently and locally, thereby reducing waste while moving away from non-renewables.




```{r, echo=FALSE, cache=FALSE, fig.align='left', fig.height=4.5, fig.width=9, results='show'}



# WESTERN EURO DATA HOUR

fr = read.csv("eurodata/fr.csv", header =TRUE, stringsAsFactors = FALSE)
fr = na.omit(fr)
fr$hour = substr(fr$end,11,nchar(fr$end)-12)
fr$year = substr(fr$end,1,nchar(fr$end)-21)
fr  = aggregate(load ~ hour + year, data = fr, mean)
df = fr
setwd("eurodata/")
temp = list.files(pattern="*.csv")
for (i in 1:length(temp)){
  fr = read.csv(temp[i], header =TRUE, stringsAsFactors = FALSE)
  fr = na.omit(fr)
  fr$hour = substr(fr$end,11,nchar(fr$end)-12)
  fr$year = substr(fr$end,1,nchar(fr$end)-21)
  fr  = aggregate(load ~ hour + year, data = fr, mean)
  fr[,paste0(temp[i])] = fr$load
  df = left_join(df, fr, by=c("hour","year"))
}
df = df[, -grep("load", colnames(df))]
colnames(df) = c('hour','year', 'Austria', 'Belgium', 'Switzerland', 'Germany', 'Denmark', 'Spain', 'France', 'UK', 'Ireland', 'Italy', 'Luxembourg', 'Netherlands', 'Norway', 'Portugal','Sweden')

eurohourwide = gather(df, country, load, Austria:Sweden, factor_key=TRUE)
eurohourwide = eurohourwide[-3]

country = c('Austria', 'Belgium', 'Switzerland', 'Germany', 'Denmark', 'Spain', 'France', 'UK', 'Ireland', 'Italy', 'Luxembourg', 'Netherlands', 'Norway', 'Portugal','Sweden')

eurohourwide <- eurohourwide[order(eurohourwide$year), ]



# build up interactive element, the filter to the two groups
button_list <- lapply(1:length(country), function(x){
  list(method = "restyle",
       args = list("transforms[0].value", country[x]),
       label = country[x])
})

# fr = read.csv("fr.csv", header =TRUE, stringsAsFactors = FALSE)
# fr = na.omit(fr)
# fr$hour = substr(fr$end,11,nchar(fr$end)-12)
# fr$year = substr(fr$end,1,nchar(fr$end)-21)
# fr  = aggregate(load ~ hour + year, data = fr, mean

p <- plot_ly(data = eurohourwide, x = ~hour, y = ~load, type = 'scatter', text = ~year, hoverinfo =~as.factor(year),
             mode = 'lines', 
             color = ~as.factor(year), alpha = 0.7,
             transforms = list( list(
                            type = 'filter',
                            target = ~country,
                            operation = '=',
                            value = unique(eurohourwide$country)[1]
      ))) %>% layout(
        title = paste0('Intraday Energy Consumption'),
         xaxis = list(title = 'Hour of Day'),
         yaxis = list(title = 'MW of Energy'),
    updatemenus = list(
      list(
  xanchor = 'left',
  yanchor = "top",
  pad = list('r'= 0, 't'= 10, 'b' = 10),
  x = 0,
  y = 1.27,
        type = 'dropdown',
        active = 0,
        buttons = button_list
        )
      )
    )
  
p <- plotly_build(p)

# p = p %>% layout(title = 'Intraday Energy Consumption',
#          xaxis = list(title = 'Time'),
#          yaxis = list(title = 'MW of Energy'))
p 



```



<!-- <div style="text-align: center;"><iframe width="560" height="315" src="https://www.youtube.com/embed/YYLzss58CLs" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe></div> -->


<center> <h2>**Production Function**: An experimental approach to detect patterns in electricity demand</h2> </center>

Firstly, let’s take a look at how COVID-19 has impacted Victoria’s electricity demand by plotting the moving average of active cases vs electricity demand alongside significant policies put in place. I **hypothesize** that most energy consumption can be attributed to weather using heating & cooling infrastructure. People will use electricity from home during lockdown rather than at their workplace resulting in a minimal difference. Secondly, large businesses make up most demand for electricity, and hence there should be no discernible effects unless these large businesses closed down. An exploration into residential & commercial electricity demand by [Energy Networks Australia](https://www.energynetworks.com.au/news/energy-insider/2020-energy-insider/commercial-down-v-residential-up-covid-19s-electricity-impact/) showed up to a 15% increase in residential use during mid-day compared to the same time in 2019. In comparison, there was up to a 19% decrease in consumption by small-medium enterprise businesses and 8% decrease in large businesses.


<!-- https://www.dhhs.vic.gov.au/victorian-coronavirus-covid-19-data -->

<center><h4>7 Day Moving Average of Active COVID-19 Cases vs Demand of Electricity Over Time</h4></center>
```{r p45, echo=FALSE, fig.align='left', fig.height=4.5, fig.width=9, results='show'}

covid = read.csv("ActiveGSG_Full_Data_data.csv")
covid$Date = as.POSIXct(covid$ï..Day.of.Date, format="%B %d, %Y")
covid = covid[2:3]


aus = read.csv("ausdata/VIC/PRICE_AND_DEMAND_201801_VIC1.csv", header =TRUE, stringsAsFactors = FALSE)
aus$SETTLEMENTDATE = as.POSIXct(aus$SETTLEMENTDATE, format="%Y/%m/%d %H:%M:%S")
aus$SETTLEMENTDATE   = strftime(aus$SETTLEMENTDATE, "%Y:%m:%d %H:00:00") %>% as.character() %>% as.POSIXct(format="%Y:%m:%d")
aus = aggregate(aus["TOTALDEMAND"], by=aus["SETTLEMENTDATE"], sum)
aus = aus %>% filter(TOTALDEMAND > 10000)
temp = list.files("ausdata/VIC/",pattern="*.csv")
for (i in 1:length(temp)){
  ausx = read.csv(paste0("ausdata/VIC/",temp[i]), header = TRUE, stringsAsFactors = FALSE)
  ausx$SETTLEMENTDATE = as.POSIXct(ausx$SETTLEMENTDATE, format="%Y/%m/%d %H:%M:%S")
  ausx$SETTLEMENTDATE   = strftime(ausx$SETTLEMENTDATE, "%Y:%m:%d %H:00:00") %>% as.character() %>% as.POSIXct(format="%Y:%m:%d")
  ausx = aggregate(ausx["TOTALDEMAND"], by=ausx["SETTLEMENTDATE"], sum)
  ausx = ausx %>% filter(TOTALDEMAND > 10000)
  aus = rbind(aus, ausx)
}
aus =  aus[(aus$SETTLEMENTDATE >= min(covid$Date) & aus$SETTLEMENTDATE <= max(covid$Date)),]
colnames(aus) = c("Date", "DEMAND")



data = merge(covid, aus,by = "Date",all = TRUE)

myfun = function(x){ rollmean(x, k = 7, fill = NA, align = "right")}
data = data %>% mutate_each(funs(myfun), Active, DEMAND)


m1 <- data[data$Date =="2020-03-16", ]
a <- list(
  x = log10(m1$Active),
  y = m1$DEMAND,
  text = "<b>March 16th</b>\nA state of emergency \nwas declared",
  xref = "x",
  yref = "y",
  showarrow = TRUE,
  arrowhead = 7,
  ax = -20,
  ay = -40
)

m2 <- data[data$Date =="2020-06-20", ]
b <- list(
  x = log10(m2$Active),
  y = m2$DEMAND,
  text = "<b>June 20th</b>\nVictorian Government re-tightened \nrestrictions on household gatherings",
  xref = "x",
  yref = "y",
  showarrow = TRUE,
  arrowhead = 7,
  ax = 100,
  ay = -40
)

m3 <- data[data$Date =="2020-07-9", ]
c <- list(
  x = log10(m3$Active),
  y = m3$DEMAND,
  text = "<b>July 9th</b>\nMetropolitan Melbourne and the \nShire of Mitchell would \nre-enter lockdown",
  xref = "x",
  yref = "y",
  showarrow = TRUE,
  arrowhead = 7,
  ax = -10,
  ay = -40
)

m4 <- data[data$Date =="2020-08-2", ]
d <- list(
  x = log10(m4$Active),
  y = m4$DEMAND,
  text = "<b>August 2nd</b>\nA state of disaster \nis declared",
  xref = "x",
  yref = "y",
  showarrow = TRUE,
  arrowhead = 7,
  ax = -20,
  ay = 40
)

p = plot_ly(data = data ,x = ~Active, y = ~DEMAND, 
        mode = 'marker+lines', marker = list(color = colorRampPalette(brewer.pal(10,"Spectral"))(length(data$Date))),
        line = list(color = '#000000',alpha = 0.5 ),
        text = ~paste(Date,'</br></br>','TOTAL DEMAND (MW):', DEMAND,'</br>',
                              '7 DMA COVID-19 CASES: ',Active)) %>% 
  layout( xaxis = list(type = "log",title="7 Day Moving Average of Active COVID-19 Cases"),
          yaxis = list(title="7 Day Moving Average of Electrcity Demand (MW)")) %>% layout(annotations = a)
p = p %>% layout(annotations = b )   %>% layout(annotations = c)  %>% layout(annotations = d)

p
```
*Note: The change in colour is to help visualise time increasing*

The figure above shows the timeseries (rainbow gradient) within a scatter plot of active COVID-19 cases versus electricity demand. It is not evident that any of the 4 major policy impacts resulted in a higher or lower electricity consumption. The changes in demand are more so attributed to seasonality. Next, we will explore which features may be attributable to electricity production. There are too many variables to explore in detail on this page, however, I have plotted below the electricity demand vs price with time filters to explore seasonality in the data.  

<center><h4>Random Sample 5000 From 2018-2020 Victoria, Australia To Observe Seasonality In Demand & Price</h4></center>

```{r p4, echo=FALSE, fig.align='left', fig.height=4.5, fig.width=9, results='show'}

aus = read.csv("ausdata/VIC/PRICE_AND_DEMAND_201801_VIC1.csv", header =TRUE, stringsAsFactors = FALSE)
temp = list.files("ausdata/VIC/",pattern="*.csv")
for (i in 1:length(temp)){
  ausx = read.csv(paste0("ausdata/VIC/",temp[i]), header = TRUE, stringsAsFactors = FALSE)
  aus = rbind(aus, ausx)
}
aus = aus[c(-1,-5)]
aus$SETTLEMENTDATE = as.POSIXct(aus$SETTLEMENTDATE, format="%Y/%m/%d %H:%M:%S")
aus$SETTLEMENTDATE   = strftime(aus$SETTLEMENTDATE, "%Y:%m:%d %H:00:00") %>% as.character() %>% as.POSIXct(format="%Y:%m:%d %H:%M:%S")
aus$hour = unclass(as.POSIXlt(aus$SETTLEMENTDATE))$hour
aus$mday = unclass(as.POSIXlt(aus$SETTLEMENTDATE))$mday
aus$wday = unclass(as.POSIXlt(aus$SETTLEMENTDATE))$wday
aus$yday = unclass(as.POSIXlt(aus$SETTLEMENTDATE))$yday
aus$mon = unclass(as.POSIXlt(aus$SETTLEMENTDATE))$mon

x= unclass(as.POSIXlt(aus$SETTLEMENTDATE))

aus = sample_n(aus, 5000)
require(plyr)
aus$mon <- mapvalues(aus$mon, 
          from=c(0,1,2,3,4,5,6,7,8,9,10,11), 
          to=c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec"))

aus$wday <- mapvalues(aus$wday, 
          from=c(0,1,2,3,4,5,6), 
          to=c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"))

library(crosstalk)




shared_df <- SharedData$new(aus)
bscols(widths = c(3,NA),
  list(
    filter_select("mon", "Month", shared_df, ~mon),
        # filter_checkbox("wday", "Day", shared_df, ~wday, inline = TRUE),
    filter_select("wday", "Day", shared_df, ~wday),
    filter_slider("hour", "Hour", shared_df, ~hour, width = "100%")
  ),

  plot_ly() %>% 
  add_trace( data = shared_df , x = ~RRP, y = ~TOTALDEMAND, type = 'scatter', color = ~factor(wday), colors=  c("#cb997e", "#689D56", "#F0C902", "#CD5300", "#4959E7", "#A60900"), alpha =0.5,
             mode = 'markers' )%>% 
  layout( xaxis = list(type = "log"), legend = list(orientation = 'h'),dragmode='pan')
)


```
An experimental approach to detect change would be to target several contributing factors to electricity demand that can be read in real time, such as weather and google trend data as a proxy of different sorts of activity. Conclusively, I aimed to explore various avenues of electricity demand to find variables that may be attributable to changes in demand. Through these insights I hope to find patterns that can provide actionable business & residential applications for the COVID normal periods & beyond.

<center><h4>Extra Content</h4></center>

Other plots such as weather, mobility & economic activity can be found on the data2app page also localised to Victoria, Australia. I’ve used live google search volume for certain keywords as a proxy for mobility & economic activity. The weather is read in live from the Bureau of Meteorology. In this exploration, I aim to only use live data sources so when incorporated within a business model, actionable insights can be obtained immediately.  

\[x_1 = weatherForecast, x_2 = weekOfYear, x_3 = dayOfWeek \]
\[x_4 = hourOfDay, x_5 = holidays, x_6 = location \]
\[x_7 = mobility, x_8 = economic Activity,x_9 = solar Panel Purchases\]
 
\[energyProduction = f(x_1, ... , x_n)\]

Sample experiments are displayed in the extras page, including a simple SARIMAX forecast, t-SNE plot & Benford’s law. My current explorations are in change point analysis and exploring what actionable insights can be made from electricity demand data outside of forecasting.

<!-- <div style="text-align: center;"><iframe width="560" height="315" src="https://www.youtube.com/embed/XXjlR2OK1kM" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe></div> -->


```{r , echo=FALSE, cache=FALSE, fig.align='left', fig.height=4.5, fig.width=9, results='show'}

# aus = read.csv("ausdata/VIC/PRICE_AND_DEMAND_201801_VIC1.csv", header =TRUE, stringsAsFactors = FALSE)
# temp = list.files("ausdata/VIC/",pattern="*.csv")
# for (i in 1:length(temp)){
#   ausx = read.csv(paste0("ausdata/VIC/",temp[i]), header = TRUE, stringsAsFactors = FALSE)
#   aus = rbind(aus, ausx)
# }
# aus = aus[c(-1,-5)]
# aus$SETTLEMENTDATE = as.POSIXct(aus$SETTLEMENTDATE, format="%Y/%m/%d %H:%M:%S")
# aus$SETTLEMENTDATE   = strftime(aus$SETTLEMENTDATE, "%Y:%m:%d %H:00:00") %>% as.character() %>% as.POSIXct(format="%Y:%m:%d %H:%M:%S")
# aus2018 = subset(aus, SETTLEMENTDATE >= "2018-01-01" & SETTLEMENTDATE <= "2018-08-31")
# aus2019 = subset(aus, SETTLEMENTDATE >= "2019-01-01" & SETTLEMENTDATE <= "2019-08-31")
# aus2020 = subset(aus, SETTLEMENTDATE >= "2020-01-01" & SETTLEMENTDATE <= "2020-08-31")

# aus2019$MONTH  = strftime(aus2019$SETTLEMENTDATE ,"%m") %>% as.character()
# aus2019$DAY  = strftime(aus2019$SETTLEMENTDATE, "%Y:%m:%d %H:00:00") %>% as.character() %>% as.POSIXct(format="%Y:%m:%d %H:%M:%S")
# 
# aus2020$MONTH  = strftime(aus2020$SETTLEMENTDATE ,"%m") %>% as.character()
# # aus2020$DAY  = strftime(aus2020$SETTLEMENTDATE, "%Y:%m:%d %H:00:00") %>% as.character() %>% as.POSIXct(format="%Y:%m:%d %H:%M:%S")
# aus2018 = aggregate(TOTALDEMAND~SETTLEMENTDATE,data=aus2018,sum)
# # x1 = aggregate(RRP~DAY+MONTH,data=aus2019,sum)
# aus2019 = aggregate(TOTALDEMAND~SETTLEMENTDATE,data=aus2019,sum)
# # y1 = aggregate(RRP~DAY+MONTH,data=aus2020,sum)
# aus2020 = aggregate(TOTALDEMAND~SETTLEMENTDATE,data=aus2020,sum)

# 
# p = plot_ly() %>%
#   add_trace( data = y1 , x = ~DAY, y = ~RRP, type = 'scatter',
#              mode = 'lines',  color ="#blue", name = '2020 RRP', alpha = 0.7)  %>%
#   add_trace( data = y2 , x = ~DAY, y = ~TOTALDEMAND, type = 'scatter',
#              mode = 'lines',  color ="#red", name = '2020 DEMAND', alpha = 0.7) %>% layout(yaxis = list(type = "log"))
# q = plot_ly() %>%
#   add_trace( data = x1 , x = ~DAY, y = ~RRP, type = 'scatter',
#              mode = 'lines',  color ="#blue", name = '2019 RRP', alpha = 0.7)  %>%
#   add_trace( data = x2 , x = ~DAY, y = ~TOTALDEMAND, type = 'scatter',
#              mode = 'lines',  color ="#red", name = '2019 DEMAND', alpha = 0.7) %>% layout(yaxis = list(type = "log"))
# # 
# # subplot(p,q, nrows=2)
# aus2018$week  = strftime(aus2018$SETTLEMENTDATE  ,"%V")
# aus2018$day  = strftime(aus2018$SETTLEMENTDATE, "%u")
# aus2018$hour  = strftime(aus2018$SETTLEMENTDATE, "%H")
# 
# aus2019$week  = strftime(aus2019$SETTLEMENTDATE  ,"%V")
# aus2019$day  = strftime(aus2019$SETTLEMENTDATE, "%u")
# aus2019$hour  = strftime(aus2019$SETTLEMENTDATE, "%H")
# 
# aus2020$week  = strftime(aus2020$SETTLEMENTDATE  ,"%V")
# aus2020$day  = strftime(aus2020$SETTLEMENTDATE, "%u")
# aus2020$hour  = strftime(aus2020$SETTLEMENTDATE, "%H")
# 
# 
# ausdiff20 = merge(aus2019, aus2020, by=c("week","day","hour"))
# ausdiff20$diff = (ausdiff20$TOTALDEMAND.y / ausdiff20$TOTALDEMAND.x)*100 -100
# ausdiff20[ausdiff20 == Inf] <- NA
# 
# ausdiff19 = merge(aus2018, aus2019, by=c("week","day","hour"))
# ausdiff19$diff = (ausdiff19$TOTALDEMAND.y / ausdiff19$TOTALDEMAND.x)*100 -100
# ausdiff19[ausdiff19 == Inf] <- NA
# 
# # ausdiff[order(ausdiff$SETTLEMENTDATE.y),]
# p = plot_ly() %>%
#   add_trace( data = ausdiff20 , x = ~SETTLEMENTDATE.y, y = ~diff, type = 'scatter',
#              mode = 'lines',  color ="#blue", name = '20-19 DIFF', alpha = 0.7) 
# q = plot_ly() %>%
#   add_trace( data = ausdiff19 , x = ~SETTLEMENTDATE.y, y = ~diff, type = 'scatter',
#              mode = 'lines',  color ="#red", name = '19-18 DIFF', alpha = 0.7)
# 
# subplot(p,q,nrows=2) 

```










```{r , echo=FALSE, cache=FALSE, fig.align='left', fig.height=4.5, fig.width=9, results='show'}



```




```{r , echo=FALSE, cache=FALSE, fig.align='left', fig.height=4.5, fig.width=9, results='show'}



```




```{r , echo=FALSE, cache=FALSE, fig.align='left', fig.height=4.5, fig.width=9, results='show'}



```














